### 2016-09-30 comparison_with_mma.tex
Grammar and wording

Mathematica can associate attributes to its atoms.
Attributes may define mathematical properties and behavior of the nodes
associated to the atom.
In SymPy, the usage of static class fields is roughly similar to Mathematica's
attributes, though other programming patterns may also be used to achieve an
equivalent behavior such as class inheritance.

@@

Unlike SymPy, Mathematica's expressions are mutable:
one can change parts of the expression tree without the need of
creating a new object.
The mutability of Mathematica expressions allows for a lazy updating of any references
to a given data structure.

@@

Regarding associative expressions,
SymPy handles associativity of sums and products by automatically flattening them,
Mathematica specifies the \texttt{Flat} attribute on the expression type.

@@

In[3]:= x + Sin[t]^2 + y + Cos[t]^2
Out[3]= 1 + x + y
\end{verbatim}
This expression in Mathematica defines a substitution rule that overloads
the functionality of the \texttt{Plus} node (the node for additions in Mathematica).
A symbol with a trailing underscore is treated as a wildcard.
Although one may wish to keep this identity unevaluated, this example clearly
illustrates the potential to define
one's own immediate transformation rules.
In SymPy, the operations constructing the addition node in the expression tree
are Python class constructors
and cannot be modified at runtime.\footnote{Nonetheless, Python supports monkey
patching but it is a discouraged programming pattern.}
The way SymPy deals with extending the missing runtime overloadability functionality
is by subclassing the node types: subclasses may redefine the class constructor
to yield the proper extended functionality.

>>>>

Mathematica can associate attributes to its atoms.
Attributes may define mathematical properties and behavior of the nodes
associated to the atom.
In SymPy, the usage of static class fields is roughly similar to Mathematica's
attributes, though other programming patterns may also be used to achieve an
equivalent behavior such, as class inheritance.

@@

Unlike SymPy, Mathematica's expressions are mutable:
one can change parts of the expression tree without the needing to
create a new object.
The mutability of Mathematica expressions allows for a lazy updating of any references
to a given data structure.

@@

Regarding associative expressions,
SymPy handles associativity of sums and products by automatically flattening them.
Mathematica specifies the \texttt{Flat} attribute on the expression type.

@@

In[3]:= x + Sin[t]^2 + y + Cos[t]^2
Out[3]= 1 + x + y
\end{verbatim}
This expression in Mathematica defines a substitution rule that overloads
the functionality of the \texttt{Plus} node (the node for additions in Mathematica).
A symbol with a trailing underscore is treated as a wildcard.
Although one may wish to keep this identity unevaluated, this example clearly
illustrates the potential to define
one's own immediate transformation rules.
In SymPy, the operations constructing the addition node in the expression tree
are Python class constructors
and cannot be modified at runtime.\footnote{Python does support monkey
patching, but it is a discouraged programming pattern.}
The way SymPy deals with extending the missing runtime overloadability functionality
is by subclassing the node types: subclasses may redefine the class constructor
to yield the proper extended functionality.
